---
title: "DVCR Forum with MCRs (September 2022)"
subtitle: "Summary of Responses to RDS Survey: Relevant to Forum"
#author: "Jen Beaudry"
#date: "29/09/2022"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
    - \usepackage{caption}
---

```{r setup, include=FALSE}

### NOTE: USE THIS FOR THE MINIMAL REPORT FOR ROB ###

knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE, 
                      eval = TRUE)

# REMEMBER: Until you figure out parameterized reports, you'll have to manually 
  # select which chunks to run and will need to delete the 'empty pages' that 
  # aren't included in Rob's report

```

```{r functions, include = FALSE}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position"))
}

```

```{r library, include=FALSE}

library(here)
library(tidyverse)
library(kableExtra)
library(RColorBrewer)

```

```{r load data, include=FALSE}

df <- read_csv(here::here("data", "mcr_forum_processed.csv"), lazy = FALSE)

```

We asked our attendees four questions. One was about the forum, two were about
their training and development needs, and one was an open-ended question giving 
them an opportunity to tell us anything else they wanted us to know. The first and 
last questions are most relevant to the DVC(R), Dean of Graduate Research, and 
Director of Research Development and Support.

\captionsetup[table]{labelformat=empty}

## Question 1
What would you like to see in future fora with the DVC(R)?

```{r table for forum ideas for Rob, include=TRUE}

# set this to TRUE and all other eval to FALSE to spit out report for Rob re
  # DVCR fora ideas. We need to run this separately so the table includes the 
  # response numbers rather than the ID numbers.

# put relevant data in a tibble
forum_ideas <- df %>% 
  dplyr::select(c(id,`forum ideas`)) %>% 
  filter(!`forum ideas` == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(forum_ideas$id))
ns <- c(resp_n, total_n) 

forum_ideas <- forum_ideas %>% 
  dplyr::select(c(responses, `forum ideas`))

knitr::kable (
  forum_ideas,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("Response #", "MCR Forum Ideas"),
  caption =
    sprintf("Responses from %s completed surveys", paste(ns, collapse = " people from ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 

# use different styling to repeat the header

```


\newpage
\captionsetup[table]{labelformat=empty}

## Question 2
Is there anything else you would like us to know?

```{r table for anything else for Rob, include = TRUE}

# use for report for Rob

# put relevant data in a tibble
anything <- df %>% 
  dplyr::select(c(id,`anything else`)) %>% 
  filter(!`anything else` == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(anything$id))
ns <- c(resp_n, total_n) 

anything <- anything %>% 
  dplyr::select(c(responses, `anything else`))

knitr::kable (
  anything,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("Response #", "Other Ideas"),
  caption =
    sprintf("Responses from %s completed surveys", paste(ns, collapse = " people from ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 

# use different styling to repeat the header

```

