---
title: "DVCR Forum with MCRs (September 2022)"
subtitle: "Summary of Responses to RDS Survey: Complete Report"
#author: "Jen Beaudry"
#date: "29/09/2022"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
    - \usepackage{caption}
---

```{r setup, include=FALSE}

### NOTE: USE THIS FOR THE FULL REPORT ###

knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE, 
                      eval = TRUE)

# REMEMBER: Until you figure out parameterized reports, you'll have to manually 
  # select which chunks to run and will need to delete the 'empty pages' that 
  # aren't included in Rob's report

```

```{r functions, include=FALSE}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position"))
}

```

```{r library, include=FALSE}

library(here)
library(tidyverse)
library(kableExtra)
library(RColorBrewer)

```

```{r load data, include=FALSE}

df <- read_csv(here::here("data", "mcr_forum_processed.csv"), lazy = FALSE)

```

We asked our attendees four questions. One was about the forum, two were about
their training and development needs, and one was an open-ended question giving 
them an opportunity to tell us anything else they wanted us to know. 

\captionsetup[table]{labelformat=empty}

## Question 1
What would you like to see in future fora with the DVC(R)?

```{r table for forum ideas}

# use for complete report not report for Rob

# put relevant data in a tibble
forum_ideas <- df %>% 
  dplyr::select(c(id,`forum ideas`)) %>% 
  filter(!`forum ideas` == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(forum_ideas$id))
ns <- c(resp_n, total_n) 

forum_ideas <- forum_ideas %>% 
  dplyr::select(c(id, `forum ideas`))

knitr::kable (
  forum_ideas,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "MCR Forum Ideas"),
  caption =
    sprintf("Responses from %s completed surveys", paste(ns, collapse = " people from ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 
# use different styling to repeat the header


```


\newpage
## Question 2
We are considering expanding our offerings in the future. Please indicate your interest 
in any of these topics:
\vskip 0.3in

```{r creating tibbles for all training responses, include=FALSE}

# get total n to calculate percentages

total_n <- length(unique(df$id))

# create tibbles for each training option so I can create stacked bar charts

os <- df %>% 
  mutate(response = `open science`, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Open science", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))


ldr <- df %>% 
  mutate(response = `leadership skills`, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Leadership skills", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))


prod <- df %>% 
  mutate(response = `research productivity`, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Research productivity", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))

e_i <- df %>% 
  mutate(response = `engagement and impact`, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Engagement and impact", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))

well <- df %>% 
  mutate(response = `well-being issues`, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Well-being issues", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))

pitch <- df %>% 
  mutate(response = `pitching research`, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Pitching research", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))

grant <- df %>% 
  mutate(response = grantmanship, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Grantsmanship", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))

plan <- df %>% 
  mutate(response = `career planning`, .keep = "unused") %>% 
  dplyr::count(response) %>% 
  mutate(training = "Career planning", .before = response) %>% 
  mutate(percentage = round (n/(total_n)*100))


# join the tibbles

train <- os %>% 
  full_join(ldr) %>% 
  full_join(prod) %>% 
  full_join(e_i) %>% 
  full_join(well) %>%
  full_join(pitch) %>% 
  full_join(grant) %>% 
  full_join(plan)

```

```{r plot the training responses}

# rename NAs  [might choose to delete them]
  # actually keeping them as NAs for now so we can make them grey in the plot

# train[is.na(train)] <- "No response"

# Relevel the responses [changes order in ggplot, but not the dataframe]
train$response <- factor (train$response, levels = c("I would attend",
                                           "I might attend", 
                                           "I would not attend"))

# plot it
ggplot(train, aes(fill = response, y = percentage, x = training)) +
  geom_bar(position="fill", stat="identity", colour = "black") +
  scale_fill_brewer(palette = "Blues", na.value = "grey50", direction = -1, 
                    labels = c("I would attend", "I might attend", "I would not attend", "No response")) +
  labs (x = element_blank(),
        y = "Percentage") +
  theme_classic() +
theme(legend.title = element_blank()) +
    coord_flip() +
   # scale_x_discrete(labels = c("Pre-publication\n Archiving", "Open Data", "Open\n Materials/Code", "Preregistration")) +
  scale_y_continuous(labels = c("0", "25", "50", "75", "100"))

```

\newpage
\captionsetup[table]{labelformat=empty}

## Question 3
What other researcher training and development opportunities would you like to see
at Flinders?

```{r table for other training}

# put relevant data in a tibble
other_training <- df %>% 
  dplyr::select(c(id,`other training`)) %>% 
  filter(!`other training` == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(other_training$id))
ns <- c(resp_n, total_n) 

other_training <- other_training %>% 
  dplyr::select(c(id, `other training`))

knitr::kable (
  other_training,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "Other Training Ideas"),
  caption =
    sprintf("Responses from %s completed surveys", paste(ns, collapse = " people from ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 
# use different styling to repeat the header


```


\newpage
\captionsetup[table]{labelformat=empty}

## Question 4
Is there anything else you would like us to know?

```{r table for anything else}

# put relevant data in a tibble
anything <- df %>% 
  dplyr::select(c(id,`anything else`)) %>% 
  filter(!`anything else` == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(anything$id))
ns <- c(resp_n, total_n) 

anything <- anything %>% 
  dplyr::select(c(id, `anything else`))

knitr::kable (
  anything,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "Other Ideas"),
  caption =
    sprintf("Responses from %s completed surveys", paste(ns, collapse = " people from ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position")) 
# use different styling to repeat the header

```

